Interactive dashboard to monitor the COVID-19 outbreak

### 2022-04-20 manuscript_covid19dashboard.tex
Updated the paper
Updated paper

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.54}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.46}}@{}}
\toprule
\textbf{Data} & \textbf{Type of graphics} \\
\midrule
\endhead
Daily COVID-19 confirmed & Time series plots \hfill\break \\
Daily COVID-19 recovered cases by time & Time series plots
\hfill\break \\
Daily COVID-19 death cases by time & Time series plots \hfill\break \\
Total COVID-19 confirmed cases by time and wave & Time series plots
annotated with vertical lines to denote significant milestones
\hfill\break \\
Total COVID-19 death cases by time and wave & Histogram \hfill\break \\
Distribution of COVID-19 patients by districts & Tile map, Choropleth
maps, Dorling Cartogram, heatmaps \hfill\break \\
Total vaccination by first dose and second dose & Time series plot
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
\bottomrule
\end{longtable}

@@

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\leavevmode\hypertarget{ref-who}{}%
{``{WHO Coronavirus (COVID-19) Dashboard}.''} 2021.
\url{https://covid19.who.int/?gcl\%0Aid=CjwKCAjwvuGJBhB1EiwACU1Aia9pAaNLOkBMS2KVlSqXptskt1t46b7_bNv6vpTt_HjvXfrnDSrWxoCE3sQAvD_\%0ABwE}.

>>>>

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.54}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.46}}@{}}
\toprule
\textbf{Data} & \textbf{Type of graphics} \\
\midrule
\endhead
Daily COVID-19 confirmed & Time series plots \hfill\break \\
Daily COVID-19 recovered cases by time & Time series plots
\hfill\break \\
Daily COVID-19 death cases by time & Time series plots \hfill\break \\
Total COVID-19 confirmed cases by time and wave & Time series plots
annotated with vertical lines to denote significant milestones
\hfill\break \\
Total COVID-19 death cases by time and wave & Histogram \hfill\break \\
Distribution of COVID-19 patients by districts & Tile map, Choropleth
maps, Dorling Cartogram, heatmaps \hfill\break \\
Total vaccination by first dose and second dose & Time series plot
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
Comparison of cases with in Sri Lanka with Top 10 countries &
Cummulative cases by time, Log of cummulative cases by time, stacked bar
chart \hfill\break \\
Spread of COVID-19 around the world & Choropleth maps \hfill\break \\
\bottomrule
\end{longtable}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\leavevmode\hypertarget{ref-who}{}%
{``{WHO Coronavirus (COVID-19) Dashboard}.''} 2021.
\url{https://covid19.who.int/region/amro/country/us}.

@@
